Individual heterogeneity in the functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-25 Manuscript.Rmd
update to sliding window figure

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
feedback <- FALSE # show permutation progress?

@@

@@

# For each permutation, reassign the study labels, maintaining the original number of studies per condition
nullDist <- mclapply(seq(nPerms), function(data) {metaPerm()})

@@

# results!
# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.01)
# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p < 0.05, R: p < 0.0001)
# v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
# null 95th-q chi <- 9.11 (varies; this was done ith 100 but resembles the 5k one)

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded.", echo=FALSE, message = FALSE}
# code to generate plot
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
  geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  scale_y_continuous(limits = c(0,1)) +
  theme_classic()

SC_FVvPDMN_plot

#include_graphics("./Images/SW_props.png")

>>>>

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
permuting <- FALSE # show permutation progress?

@@

# optional because it can take a long time to run
if (permuting) {

@@

  # For each permutation, reassign the study labels, maintaining the original number of studies per condition
  nullDist <- mclapply(seq(nPerms), function(permutation) {metaPerm(perm = permutation)})
  nullDist <- do.call(rbind, nullDist)

@@

}
# results!
# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.01)
# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p < 0.05, R: p < 0.0001)
# v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
# null 95th-q chi <- 9.11 (varies; this was done ith 100 but resembles the 5k one)

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37). B: Proportion of times each vertex was affiliated with the DMN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DMN affiliations. Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded.", echo=FALSE, message = FALSE}
# code to generate plots

# # time series
# # this one uses the actual subject's loaded time series (not included due to space)
# n <- 4 # n of vertices to include
# tr <- 4800 
# ts <- data.matrix(t1[sample(59000, n), 1:tr])
# df <- tibble(vertex = rep(seq(n), each = tr),
#              Time = floor(rep(seq(0, tr, length.out = tr), n)),
#              Signal = matrix(ts, ncol = 1) + rep(seq(-1, 1, length.out = n), each = tr)) %>%
#   ggplot(data = df, aes(Time, Signal, group = vertex, color = as.character(vertex))) +
#     geom_line(show.legend = F, lwd = 0.2, alpha = 0.6) +
#     theme_classic()
# 
# # Fiedler Vector x proportion of times a vertex was affiliated with DMN
# SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
#   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
#   geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
#   geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
#   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
#   scale_y_continuous(limits = c(0,1)) +
#   theme_classic()
# 
# SC_FVvPDMN_plot

include_graphics("./Images/SW_props.png")
